Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-01-19 README.Rmd
uploaded more memory efficient version

This compendium was created using the [`rrtools` package by Ben Marwick](https://github.com/benmarwick/rrtools), which is ✨pure magic ✨for doing reproducible research.

>>>>

This compendium was created using the [`rrtools` package by Ben Marwick](https://github.com/benmarwick/rrtools), which is ✨ pure magic ✨ for doing reproducible research.
